---
title: "<center>Bayesian Statistics is 'Bae'</center>"
author: "<center>Wyclife Agumba Oluoch  (wyclifeoluoch@gmail.com)</center>"
date: '<center>Date: `r Sys.time()`</center>'
output:
  html_document:
    df_print: paged
  html_notebook:
    df_print: paged
bibliography: packages.bib
nocite: '@*'
---

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
packages <- c("bayesutils",
              'bayestestR',
              'insight',
              "rstanarm",
              "ggplot2")
installed_packages <- packages %in% rownames(installed.packages())
if(any(installed_packages == FALSE)){
  install.packages(packages[!installed_packages])
}
lapply(packages, library, character.only = TRUE) |> 
  invisible()
```

```{r write_bib, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
knitr::write_bib(c(
  .packages(), packages
), 'packages.bib')
```


```{r, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
model <- rstanarm::stan_glm(bsalary ~., data = bank_salary, chains = 2, iter = 10000, warmup = 5000)
posteriors <- insight::get_parameters(model)
desc <- describe_posterior(model)
print(desc)
head(get_parameters(model))
nrow(get_parameters(model))
```
```{r, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
ggplot(posteriors, aes(x = male)) +
  geom_density(fill = 'purple')
```
<font size = '6'>A visual comparison of `median`, `map_estimate`, and `mean` of posterior in **Bayesian Statistics** of `bank_salary` data.set in **`R`**. The data.set comes with `bayesutils` package [@R-bayesutils] version `r packageVersion('bayesutils')`. Modeled using `rstanarm` package [@R-rstanarm] version `r packageVersion('rstanarm')` and plotted using `ggplot2` package [@ggplot22016] version `r packageVersion('ggplot2')` in `R` Statistical package version 4.1.0 also known.a `Camp Pontanezen`</font>. 
```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(posteriors, aes(x = male)) +
  geom_density(fill = "purple") +
  # The mean in blue
  geom_vline(xintercept = mean(posteriors$male), 
             color = "blue", size = 1) +
  # The median in red
  geom_vline(xintercept = median(posteriors$male), 
             color = "red", size = 1) +
  # The MAP in purple
  geom_vline(xintercept = map_estimate(posteriors$male), 
             color = "orange", size = 1)
```
# References